A Kochen-Specker system has at least 21 vertices\\ {\small (extended abstract)}

### 2014-04-14 main.tex
conclusie

With this method, we have decided the embeddability of every squarefree
graph with minimal vertex order three of 13 vertices of less.
In particular:
\begin{comp}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal 20
    contains as a subgraph one of
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    which are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a direct proof.

\section{Conclusion and future research}
TODO

>>>>

With this method, we have decided in an hour the embeddability
of every squarefree graph with minimal vertex order three of 13
vertices of less.
In particular:
\begin{comp}
    Every squarefree graph of minimal vertex order three
    that is not 010-colorable
    of order less than or equal 20
    contains as a subgraph one of
    \begin{center}
        \includegraphics[width=120mm]{graphs/unemb-base-20.jpg}
    \end{center}
    which are unembeddable.  The left and middle graph
    are the only minimal unembeddable squarefree graph.
\end{comp}
For the first graph, we have proven directly that it is unembeddable.
See Proposition~\ref{prop:unemb-10-2}.
For the second graph, we also have a direct proof.

\section{Conclusion and future research}
Arends, Ouaknine and Wampler struggled with two problems:
enumerating candidate graphs of less than 31 vertices
and testing their embeddability.
We have verified most of their computation claims.
Then, we enumerated all candidate graphs
up to 21 vertices.
Furthermore, we have proposed a new decision procedure
which was able to decide embeddability,
for all candidate graphs we found.
Therefore, we demonstrate: a Kochen-Specker system must have at least
21 points.

Enumerating all candidate graphs of less than 31 vertices
is computationally infeasable.
To bridge the enormous the gap between 21 and 31,
requires a new insight.
For instance: another restriction on which graphs to consider.

The Reader, interested in pursuing this line of research,
is encouraged to read the master thesis\cite{a09} of Arends,
in which he discusses in detail several other
properties that a minimal KS system must enjoy, as well as
some failed attempts.
